analysis

### 2019-12-09 03_Preliminary_analysis.Rmd
Investigate the influence of propiconazole on yield

Which studies used which doses?

```{r}

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(s1_DfromFS = fungicide_application_1 - first_sign_disease,
          s2_DfromFS = fungicide_application_2 - first_sign_disease,
          s3_DfromFS = fungicide_application_3 - first_sign_disease,
          s4_DfromFS = fungicide_application_4 - first_sign_disease,
          s5_DfromFS = fungicide_application_5 - first_sign_disease) %>%
   gather(key = spray, value = n_days, s1_DfromFS, s2_DfromFS, s3_DfromFS, s4_DfromFS, s5_DfromFS)%>%
   ggplot(aes(x = spray, y = n_days))+
   geom_violin()

>>>>

This dose effect should be acknowledged in the meta-analysis. How many treatments of each dose have been investigated per trial?

```{r table_PropiDoses}
table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref), 
      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
```

Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02. Let look at the difference in proportion of yield saved in these trials.

```{r PropiDoses_TrialCompar}

boxplot(prop_YG ~ dose_ai.ha, data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
                                                    PM_MB_means$trial_ref == "mung1112/02") &
                                                    PM_MB_means$fungicide_ai == "propiconazole",])
```

This plox plot, however, indicated the previous plot might be skewed by high yielding trials.

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(s1_DfromFS = fungicide_application_1 - first_sign_disease,
          s2_DfromFS = fungicide_application_2 - first_sign_disease,
          s3_DfromFS = fungicide_application_3 - first_sign_disease,
          s4_DfromFS = fungicide_application_4 - first_sign_disease,
          s5_DfromFS = fungicide_application_5 - first_sign_disease) %>%
   gather(key = spray, value = n_days, s1_DfromFS, s2_DfromFS, s3_DfromFS, s4_DfromFS, s5_DfromFS)%>%
   ggplot(aes(x = spray, y = n_days))+
   geom_violin() +
   scale_x_discrete(labels = c("First\nSpray", "Second\nspray","Third\nspray","Fourth\nspray","Fifth\nspray"))+
   theme_usq()
